Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-07 sattose/paper.tex
Final sattose edits

Section

@@

\section{Clone Detection}\label{chap:clonedetection}
As duplication in source code is a serious problem in many software systems, many research efforts look into code clones. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. \todo{what is insufficient about these two? what triggered the need to reassess clone detectors? where are the four criteria coming from?}

\subsection{Survey on Clone Detection Tools}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze either Java or Python. Then we chose four criteria by which we considered these tools: 
\begin{enumerate}
    \item \textbf{Should find clones in any context.} We want to perform an analysis on a set of projects. In this analysis we want to be able to get a full overview of cloning in the set of projects. Some tools only find clones in specific contexts, like only method-level clones. Because of that, we want to use a clone detection tool that is able to find clones in any context.
\item \textbf{Should detect clone classes in a number of example projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Considers dependency graphs to be sure that this clone can be merged.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal. Sometimes, to verify actual equality (not just textual equality), it is required to consider resolved symbols (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to recognize the meaning of certain tokens.
\end{enumerate}

>>>>

Section \ref{chap:background} describes the background from literature that we used to conduct this study. Section \ref{chap:clonedetection} presents our clone refactoring tool proposal. Section \ref{chap:clonetypes} outlines challenges with clone type definitions and proposes solutions for them in a refactoring context. Section \ref{chap:clonecontextexpl} outlines our analysis and measurements regarding the context of code clones. Section \ref{chap:mergingdups} shows our measurements regarding the amount of clones that can be refactored through method extraction. Section \ref{chap:threatstovalidity} shows the threats to validity of this study and section \ref{chap:conclusion} draws a conclusion on our preliminary results.

@@

\section{Clone Detection}\label{chap:clonedetection}
As duplication in source code is a serious problem in many software systems, many research efforts look into code clones. Many tools have been proposed to detect various types of code clones~\cite{sheneamer2016survey, svajlenko2014evaluating}. However, these tools were not yet assessed in terms of automatically refactoring clones.

In this section, we first assess a set of modern clone detection tools for their applicability to this domain. Next, we introduce our own tool geared towards automatic clone refactoring, CloneRefactor.%Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. \todo{what is insufficient about these two? what triggered the need to reassess clone detectors? where are the four criteria coming from?}

\subsection{Survey on Clone Detection Tools}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze either Java or Python. Next we formulate the following four criteria by which we analyze these tools: 
\begin{enumerate}
    \item \textbf{Should find clones in any context.} We want to perform an analysis on a set of projects. In this analysis we want to be able to get a full overview of cloning in the set of projects. Some tools only find clones in specific contexts, like only method-level clones. Because of that, we want to use a clone detection tool that is able to find clones in any context.
\item \textbf{Should detect clone classes in a number of example projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Considers dependency graphs to be sure that this clone can be merged.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal. Sometimes, to verify actual equality (not just textual equality), it is required to consider resolved symbols (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to recognize the meaning of certain tokens.
\end{enumerate}
